---
output:
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-",
  warning = FALSE, 
  message = FALSE
)
```

# YahooTickers

[![Travis-CI Build Status](https://travis-ci.org/Reckziegel/YahooTickers.svg?branch=master)](https://travis-ci.org/Reckziegel/YahooTickers)

The goal of YahooTickers is to help users to easily get stock index constituents from [Yahoo Finance](https://finance.yahoo.com/) without having to run complicated `for` loops. This may be specially useful for users that need to repeatably test investment strategies in different markets, but also be convenient if data is needed for it's side effects (plotting).  


## Instalation

You can install FromQuandl from github with:

```{r eval = FALSE}

# install.packages("devtools")
devtools::install_github("Reckziegel/FromQuandl")

```


## Example

Suppose we want to download all the stock constituents of the Dow Jones Industrial Average Index. This can easily be done with `get_tickers()` and `get_stock()` in one pipeline.

```{r example1}
library(YahooTickers)
library(dplyr)

get_tickers("dow") %>% 
  get_stocks(., periodicity = "monthly")

```

Since the data is "tidy" it's ready to be used in conjunction with `ggplot2` and the `dplyr` verbs for further manipulation (if needed).

```{r example2}
library(YahooTickers)
library(dplyr)
library(ggplot2)

get_tickers("dow") %>% 
  get_stocks(., periodicity = "monthly") %>% 
  ggplot(aes(x = index, y = close, color = tickers)) + 
  geom_line(show.legend = FALSE, size = 1) + 
  scale_y_log10() + 
  facet_wrap(~ tickers, scales = "free_y") + 
  labs(title    = "Dow Jones Industrial Average",
       subtitle = "Monthly data from 2010-01-01 until 2018-10-25",
       caption  = "Source: Yahoo Finance",
       x        = "", 
       y        = "") 

```

Currently, `YahooTickers` supports the following stock indexes: 

* `dow`: Dow Jones Industrial Average (United States)
* `sp500`: S&P 500 (United States)
* `nasdaq`: NASDAQ Composite Index (United States)
* `nyse`: NYSE Composite Index (United States)
* `amex`: AMEX Composite Index (United States)
* `russell2000`: Russell 2000 Index (United States)
* `ftse100`: FTSE 100 Index (United Kingdom)
* `dax`: Deutsche Boerse AG German Stock (Germany)
* `cac40`: CAC 40 Index (France)
* `bel20`: BEL 20 Index (Belgium)
* `topix`: TOPIX Core 30 Index (Japan)
* `hangseng`: HangSeng Composite Index (Hong Kong)
* `sensex`: S&P BSE SENSEX Index (India)
* `jakarta`: Jakarta Stock Exchange Stock Index (Indonesia)
* `bursa`: Bursa Malaysia Bhd (Malaysia)
* `nzx50`: S&P/NZX 50 Gross Index (New Zealand) 
* `kospi`: Korea Stock Exchange KOSPI Index (south Korea)
* `taiex`: Taiwan Stock Exchange Weighted Index (Taiwan)
* `tsx`: S&P/TSX Composite Index (Canada)
* `ibovespa`: Ibovespa Brasil Sao Paulo Stock Exchange Index (Brazil)
* `ipc`: S&P/BMV IPC (Mexico)
* `ipsa`: S&P/CLX IPSA (Chile)
* `merval`: Buenos Aires Stock Exchange Merval Index (Argentina)

## A Warning

The [Yahoo Finance](https://finance.yahoo.com/) API works reasonably well, but there are cases in which does not cover or provide historical data for all stocks in an index universe. The `bel20` it's a good example: despite officially having 20 components, Yahoo Finance only maintain data for only 4. The message is clear: *always check the data after downloading!*
