---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE, warning=FALSE, message=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-",
  warning = FALSE, 
  message = FALSE
)

library(YahooTickers)
library(dplyr)

```

# YahooTickers

[![Travis build status](https://travis-ci.org/Reckziegel/YahooTickers.svg?branch=master)](https://travis-ci.org/Reckziegel/YahooTickers)
[![AppVeyor build status](https://ci.appveyor.com/api/projects/status/github/Reckziegel/YahooTickers?branch=master&svg=true)](https://ci.appveyor.com/project/Reckziegel/YahooTickers)
[![Codecov test coverage](https://codecov.io/gh/Reckziegel/YahooTickers/branch/master/graph/badge.svg)](https://codecov.io/gh/Reckziegel/YahooTickers?branch=master)

The goal of YahooTickers is to easily get stock index constituents from [Yahoo Finance](https://finance.yahoo.com/) without having to worry about complicated `for` loops. This may be useful if you wish to focus as quickly as possible in time-series *modeling*, but also convenient if data is needed for it's side effects (e.g. plotting).  

The package depends heavly on [quantmod](https://github.com/joshuaulrich/quantmod), [rsample](https://github.com/topepo/rsample), [sweep](https://github.com/business-science/sweep) and [forecast](https://github.com/robjhyndman/forecast) projects. 


## Instalation

You can install YahooTickers from github with:

```{r eval = FALSE}
# install.packages("devtools")
devtools::install_github("Reckziegel/YahooTickers")
```


## Examples

To download *all* the stock constituents of the Dow Jones Industrial Average use `get_tickers()` and `get_stocks()` in one pipeline.

```{r example1}
dow <- get_tickers(dow) %>% 
  get_stocks(., periodicity = "monthly")

dow 
```

With additional functions provided in the package it's possible to fit a model in a rolling or expanding time window. This is done by `get_models()`.

```{r example2, warning=FALSE, error=FALSE}
library(forecast)

merval_models <- get_tickers(merval) %>%
  get_stocks(
    tickers     = ., 
    periodicity = "monthly",
    quiet       = TRUE
    ) %>% 
  get_returns(
    .tbl     = ., 
    .group   = tickers, 
    .type    = log, 
    .omit_na = TRUE, 
    ret_adj  = adjusted # change col names on the fly like dplyr!
    ) %>% 
  get_models(
    .tbl        = .,
    .group      = tickers, 
    .col        = ret_adj, 
    .initial    = 100, 
    .assess     = 1, 
    .cumulative = TRUE, 
    .fun        = ets
    ) 

merval_models

```

In this case, the the [ETS](http://pkg.robjhyndman.com/forecast/reference/ets.html) function was used to fit the first 100 observations on a expanding window, `.cumulative = TRUE`. The output contains the fitted parameters, selection criterias, as some traditional in-sample error metrics. 

To extract the true out-of-sample forecasts use `get_forecasts()`. This function automatically identifies the `.assess` argument in `get_models()` and uses it as a target for the forecast horizon. 

```{r example3, warning=FALSE, error=FALSE}
library(forecast)

merval_models  %>% 
  get_forecasts(.)

```

Currently, `YahooTickers` supports the following stock indexes: 

* `dow`: Dow Jones Industrial Average (United States)
* `sp500`: S&P 500 (United States)
* `nasdaq`: NASDAQ Composite Index (United States)
* `nyse`: NYSE Composite Index (United States)
* `amex`: AMEX Composite Index (United States)
* `russell2000`: Russell 2000 Index (United States)
* `ftse100`: FTSE 100 Index (United Kingdom)
* `dax`: Deutsche Boerse AG German Stock (Germany)
* `cac40`: CAC 40 Index (France)
* `bel20`: BEL 20 Index (Belgium)
* `topix`: TOPIX Core 30 Index (Japan)
* `hangseng`: HangSeng Composite Index (Hong Kong)
* `sensex`: S&P BSE SENSEX Index (India)
* `jakarta`: Jakarta Stock Exchange Stock Index (Indonesia)
* `bursa`: Bursa Malaysia Bhd (Malaysia)
* `nzx50`: S&P/NZX 50 Gross Index (New Zealand) 
* `kospi`: Korea Stock Exchange KOSPI Index (south Korea)
* `taiex`: Taiwan Stock Exchange Weighted Index (Taiwan)
* `tsx`: S&P/TSX Composite Index (Canada)
* `ibovespa`: Ibovespa Brasil Sao Paulo Stock Exchange Index (Brazil)
* `ipc`: S&P/BMV IPC (Mexico)
* `ipsa`: S&P/CLX IPSA (Chile)
* `merval`: Buenos Aires Stock Exchange Merval Index (Argentina)


## A Warning

The [Yahoo Finance](https://finance.yahoo.com/) API works reasonably well but there are cases in which it does not cover historical data for all stocks in an index universe. The `bel20` it's a good example: despite officially having 20 components, Yahoo Finance only maintains data for 4 stocks. Thus, it is recommended to **always check the data after downloading it!**
